### 2016-09-28 Theorem3_FP.tex
Proofs syntax update
Proof3 update
Proof9 updated as per changed syntax
cleaning up in Section 4, prior to adding new material
Complying proof with current syntax

\begin{proof}[\Cref{thm3}]
We use a game playing argument to prove this theorem in the ROM. In $\game{0}$, the $\Hash$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO). For every distinct query, $\Hash$ returns a random value sampled from $[m]$. Here, the adversary $A$, along with $\Rep$ and $\Qry$ are given access to $\Hash$. It can be seen that, $\game{0}$ exactly simulates the correctness game of $\Pi_{\mathrm{Bloom}}$. So, $\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A) = 1}$.

$\game{1}$ is exactly same as $\game{0}$ except the $\Qry$ oracle is replaced by the code of $\Qry$, whereas in $\game{2}$, the $\Test$ oracle returns the hash values back to the adversary along with $q_x(S)$ and output of the $\Qry$ oracle. $\game{3}$ on the other hand, returns all the $k$ hash values for any query. This results in adversary getting $(k-1)$ hash values for free as we charge the adversary for a single query. Since $k$ is likely to be very small compared to the number of queries the adversary makes, this would not affect the analysis in any significant manner. Also, in real world, RO will be a hash function; hence the adversary can perform local computations to get the hash values. It can be easily seen that the output of all the games will be same. So, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1} = \Prob{\game{2}(A) = 1} = \Prob{\game{3}(A) = 1}$.

In $\game{4}$, assuming $A$ does not make any pointless queries, $\Hash$ returns $k$ random values (for each query) sampled from $[m]$. Also, we offload all of $\Test$'s computations to $\Hash$, which now maintains an $\Ans$ table to compute and save answers for each query.  For any query, $q$, the $\Test$ oracle returns answer stored at $\Ans[q]$. We also introduce the $\bad$ flag in this game. Like in the earlier proofs,  $\bad$ is set to true, if queries indexed by the r-set $\calI$ fail to be false positives, or the other queries are false-positives. $\bad$ in fact does not affect the output of $\Hash$ or the game. So, $\Prob{\game{4}(A) = 1} = \Prob{\game{3}(A) = 1}$.

$\game{5}$ is exactly same as $\game{4}$, but returns 0, if $\bad$ is set to true. It can be observed that, the total queries made to the $\Hash$ oracle by the adversary is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$). Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \frac{1}{\dbinom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.

@@

$S \getsr \distr{\calS}{}$, $\err \gets 0$\\

@@

$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\

@@

\oracle{$\TestOracle(q_x)$}\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
if $a \neq q_x(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,q_x(S) )$\\

@@

\oracle{$\HashOracle(i,q_y)$}\\

@@

if $T[i,q_y] \neq \undefined$\\
\nudge $v \gets T[i,q_y]$\\
$T[i,q_y] \gets v$\\

@@

\oracle{$\TestOracle(q_x)$}\\

@@

\nudge $h_j \gets \HashOracle(j,q_x)$\\
\nudge if $M[h_j] \neq 1$ then Return $(0, q_x(S))$\\
Return~$(1,q_x(S))$\\

@@

\nudge $h_j \gets \HashOracle(j,q_x)$\\

@@

%\nudge \nudge if $j = 1$ then Return $(0, \err, \emptystring)$\\
\nudge \nudge Return $(0, q_x(S), (h_1, \ldots, h_j))$\\

@@

Return~$(1,q_x(S), (h_1, \ldots, h_{k}) )$\\

@@

\oracle{$\TestOracle(q_x)$}\\
$M \gets\pubaux $\\
$(h_1, \ldots, h_{k}) \gets \HashOracle(q_x)$\\

@@

\nudge \nudge Return~$(0,q_x(S), (h_1, \ldots, h_{k}) )$\\

@@

\oracle{$\HashOracle(q_y)$}\\

@@

\nudge if $T[j,q_y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,q_y]$\\
\nudge $T[j,q_y] \gets v_j$\\

@@

$S \getsr \distr{\calS}{}$\\
$\err \gets 0$, $\Ans \gets \emptyset$\\
$c \gets 0$, $\bad \gets \false$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\

@@

\oracle{$\TestOracle(q_x)$}\\

@@

\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(q_x)$\\

@@

\nudge \nudge $\Ans[q_y] \gets (0, q_y(S), (v_1, \ldots, v_{k}) )$\\

@@

@@

$\Ans[q_y] \gets (1, q_y(S), (v_1, \ldots, v_{k}))$\\

>>>>

\section{Proof of \Cref{thm3}}
\label{sec:thm3_fp}
\begin{proof}[\Cref{thm3}]
We use a game playing argument to prove this theorem in the ROM. In $\game{0}$, the $\Hash$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO). For every distinct query, $\Hash$ returns a random value sampled from $[m]$. Here, the adversary $A$, along with $\Rep$ and $\Qry$ are given access to $\Hash$. It can be seen that, $\game{0}$ exactly simulates the correctness game of $\Pi_{\mathrm{Bloom}}$. So, $\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A) = 1}$.

$\game{1}$ is exactly same as $\game{0}$ except the $\Qry$ oracle is replaced by the code of $\Qry$, whereas in $\game{2}$, the $\Test$ oracle returns the hash values back to the adversary along with output of the $\Qry$ oracle. $\game{3}$ on the other hand, returns all the $k$ hash values for any query. This results in adversary getting $(k-1)$ hash values for free as we charge the adversary for a single query. Since $k$ is likely to be very small compared to the number of queries the adversary makes, this would not affect the analysis in any significant manner. Also, in real world, RO will be a hash function; hence the adversary can perform local computations to get the hash values. It can be easily seen that the output of all the games will be same. So, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1} = \Prob{\game{2}(A) = 1} = \Prob{\game{3}(A) = 1}$.

In $\game{4}$, assuming $A$ does not make any pointless queries, $\Hash$ returns $k$ random values (for each query) sampled from $[m]$. Also, we offload all of $\Test$'s computations to $\Hash$, which now maintains an $\Ans$ table to compute and save answers for each query.  For any query, $\qry$, the $\Test$ oracle returns answer stored at $\Ans[\qry]$. We also introduce the $\bad$ flag in this game. Like in the earlier proofs,  $\bad$ is set to true, if queries indexed by the r-set $\calI$ fail to be false positives, or the other queries are false-positives. $\bad$ in fact does not affect the output of $\Hash$ or the game. So, $\Prob{\game{4}(A) = 1} = \Prob{\game{3}(A) = 1}$.

$\game{5}$ is exactly same as $\game{4}$, but returns 0, if $\bad$ is set to true. It can be observed that, the total queries made to the $\Hash$ oracle by the adversary is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$) to the RO. Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \dfrac{1}{\dbinom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.

@@

$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\

@@

$\bot \getsr A^{\TestOracle}(\pubaux)$\\

@@

\oracle{$\TestOracle(\qry_x)$}\\
if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup \{\qry_x\}$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,\qry_x)$\\
if $a \neq \qry_x(S)$ then \\
\nudge $\err \gets \err + 1$\\
Return~$a$\\

@@

\oracle{$\HashOracle(i,\qry_y)$}\\

@@

if $T[i,\qry_y] \neq \undefined$\\
\nudge $v \gets T[i,\qry_y]$\\
$T[i,\qry_y] \gets v$\\

@@

\oracle{$\TestOracle(\qry_x)$}\\
if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup \{\qry_x\}$; $M \gets\pubaux$\\

@@

\nudge $h_j \gets \HashOracle(j,\qry_x)$\\
\nudge if $M[h_j] \neq 1$ then Return 0\\
$\err \gets \err + 1$\\

@@

\nudge $h_j \gets \HashOracle(j,\qry_x)$\\

@@

\nudge \nudge Return $(0, (h_1, \ldots, h_j))$\\

@@

Return~$(1, (h_1, \ldots, h_{k}) )$\\

@@

\oracle{$\TestOracle(\qry_x)$}\\
if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup \{\qry_x\}$; $M \gets\pubaux$\\
$(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\

@@

\nudge \nudge Return~$(0, (h_1, \ldots, h_{k}) )$\\

@@

\oracle{$\HashOracle(\qry_y)$}\\

@@

\nudge if $T[j,\qry_y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,\qry_y]$\\
\nudge $T[j,\qry_y] \gets v_j$\\

@@

$c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\

@@

\oracle{$\TestOracle(\qry_x)$}\\
if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup \{\qry_x\}$\\

@@

\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\

@@

\nudge \nudge $\Ans[\qry_y] \gets (0, (v_1, \ldots, v_{k}) )$\\

@@

if $j < k$ then Return $\left(v_1,\ldots,v_k\right)$\\

@@

$\Ans[\qry_y] \gets (1, (v_1, \ldots, v_{k}))$\\
Return $\left(v_1,\ldots,v_k\right)$
